---
title: "01_EDA"
author: "ynakahashi"
date: "2018/7/30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ---- Libraries

```{r}
library(tidyverse)
library(summarytools)
```

```{r}
data_dir <- "/Users/yn250006/OneDrive - Teradata/Training/Kaggle/HomeCredit/Data/all/"
```


## ---- Description

There are 8 files for the analysis.
 - application_test.csv
 - application_train.csv
 - bureau_balance.csv
 - bureau.csv
 - credit_card_balance.csv
 - installments_payments.csv
 - POS_CASH_balance.csv
 - previous_application.csv

## ---- 1. application
### ---- Data loading
```{r}
file_01 <- "application_train.csv"
file_02 <- "application_test.csv"

dat_train <- read_csv(paste0(data_dir, file_01))
dat_test  <- read_csv(paste0(data_dir, file_02))
```


ひとまず 'summarytools' でサクッと
```{r}
dat_all <- dat_train %>% bind_rows(dat_test)
```

エディタにコピペする
```{r, results = "asis"}
# dfSummary(dat_all, plain.ascii = FALSE, style = "grid")
```



## ---- 2. previous_application
## ---- 3. bureau
## ---- 4. bureau_balance
## ---- 5. credit_card_balance
## ---- 6. installments_payments
## ---- 7. POS_CASH_balance






